Physio Denoise is a robust denoising tool for fMRI data. 
Proceeding the raw txt file of physiological data with advanced bio-signal detecting tools, 
Physio Denoise could calculate the regressors for RETROICOR model directly.
In the meanwhile, Physio Denoise has strong visualization in outputs.
Important figures in the main step are generated for users to better understand the process.
And intermediate variables are able to trace back the calculating process.
In the results, all the noise components of high contrast 
are shown in the background of a structural brain image, which
is easy to relate brain structure to the possible reasons for explaining the noise.
The spectrum of predicted noise could also be used to analyze noise in frequency domain.

However, there are still several crucial problems and concern with Physio Denoise.

First, the whole implementation of Physio Noise is based on RETROICOR model and GLM. 
The nuisance regressors in the noise model are not completely linear independent 
and may exhibit shared variance \cite{bright2017potential}.
Those correlated regressors might 
add more difficulty to interpreting the influence from each component.
One possible solution to this problem is to include additional combined regressors into the model
from both respiratory and cardiac signals. Then the influence from correlated regressors 
could be taken into consideration. 

As mentioned previously, another related problem about the potential correlation 
between nuisance regressors and real neuronal events. 
Cardiac pulsation results in brain tissue movement and 
inflow effects leading to correlated signal fluctuations primarily 
in and near large blood vessels \cite{dagli1999localization}. The movement of the chest wall during breathing results 
in magnetic field changes that distort the MR image acquired of the brain \cite{brosch2002simulation}.
Moreover, Cerebrospinal fluid (CSF) inside brain will be manipulated by both respiration and cardiac cycles.

The concern with design of Physio Denoise is applying regressors to the entire brain. 
Apparently, physiological influence cannot be removed by the use of a single nuisance regressor 
for the entire brain (such as global signal regression) due to the 
clear regional heterogeneity of the physiologically-coupled responses. \cite{chen2020resting}
Step like regional division could be applied to the data before regression, which could lead to more precise
denoising.

